PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-11-26 main.tex
Changes to end of paper.

%TRQ: \sigma is not defined.
To ensure that the boundary seen near 60 days in orbital period is not
simply a transient product of the inside-out growth throughout the
disk, we examine the time evolution of $\sigma/\Sigma$ at multiple
orbital periods. In figure \ref{fig:pl_frac_time}, the value of
$\sigma/\Sigma$ is plotted as a function of time in 10 orbital period
bins, each with a width of 10 days.
Bins interior to 60 days are shown by a dashed line, while those exterior are shown as a solid line. In all radial bins, the 
planetesimal surface density is approaching an asymptotic value. In the inner disk, this value asymptotes to zero as the 
planetesimal population entirely depletes. In the outer disk, dynamical friction between the embryos and planetesimals 
eventually throttles subsequent accretion and leaves $\sim$ 10 percent or more of the mass surface density as planetesimals. It 
should be noted that in a typical oligarchic growth scenario, where protoplanets space themselves apart by 10 $r_{h}$ and settle 
onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent of the planetesimal mass should remain out of reach of the 
protoplanets.

@@

Next, we investigate how the resulting planetesimal and protoplanet distribution
changes as we vary the initial solid surface density profile.
The final orbital period-eccentricity state of the
particles in the fdHi, fdHiSteep, fdHiShallow and fdLo simulations are shown in figure \ref{fig:surfden_profiles}, with point sizes 
indicating the relative masses of the bodies. In all cases, the inner disk is largely depleted of planetesimals, while the outer disk 
contains a bimodal population of planetesimals and embryos, with a clear separation in eccentricity between the two. Despite 
having significantly different masses, the planetary embryos formed in all simulations have remarkably similar eccentricities. This 
is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which 
offsets the fact that the initial bodies started off in a dynamically hotter state. The only exception to this is the fdLo simulation, 
where the resulting eccentricities are a couple orders of magnitude smaller. Inelastic damping likely plays an even more 
significant role here, due to the much larger masses of the initial planetesimals.

In figure \ref{fig:surfden_b}, we plot the masses of the resulting protoplanets and planetesimals in all four simulations in units of $
\tilde{b}$ (see equation \ref{eq:iso}).

As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) carries a special significance, being the  
feeding zone width that a body on a circular orbit should have. In all four simulations, the feeding zone width exceeds the 
minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days. The orbital periods at which this transition 
occurs are quite similar between simulations, despite the vastly different solid surface density profiles used. This indicates that 
the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our 
conclusion that planetesimal accretion is largely complete everywhere in the disk.

@@

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/acc_zones.png}
    \caption{For the 20 most massive bodies at the end of the fdHi simulation, the relative shape of the accretion zones for each body are shown. The hash marks indicate the present position of the body. The accretion distributions indicate the initial locations of the planetesimals that were used to assemble a body, rather than the locations at which collisions with the massive body occurred.\label{fig:acc_zones}}
\end{center}
\end{figure*}

@@

Another line of evidence pointing to a lack of gravitational scattering and orbital repulsion in the inner disk can be seen in figure \ref{fig:acc_zones}. Here, we have chosen the 20 most massive bodies from the fdHi simulation and arranged them in order of final orbital period. On each line, the black has mark indicates the present orbital period of an embryo and the gray histogram represents the initial orbital period distribution of the planetesimals which were used to construct the embryo. One should note that unlike the previous figure, this plot shows where every single bit of mass (in the form of planetesimals) originated, rather than only denoting embryo-planetesimal collisions.

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/f6f4_b.png}
    \caption{In the top panel, we show the required feeding zone sizes to produce the masses of the bodies seen
    at the end of the fdHi and fdHif4 simulations.The bottom panel shows the variation of $\alpha$ with orbital period for the 
    bodies used in each case (solid curves). The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of 
    the embryo mass distribution and isolation mass. The shaded region in the bottom panel show the values of alpha for realistic-
    sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4_b}}
\end{center}
\end{figure}

@@

To test whether a more restrictive collision model should alter the growth mode of the inner disk, we ran a smaller scale test 
using a slightly more restrictive collision model. In this case, a collision can result in one of two outcomes: if the impact velocity is 
smaller than the mutual escape velocity of the colliding particles, defined as

\begin{equation}\label{eq:v_mut}
	v_{mut, esc} = \sqrt{\frac{2 G (m_{1} + m_{2})}{r_{1} + r_{2}}},
\end{equation}

where $m_{1}, m_{2}$ and $r_{1}, r_{2}$ are the masses and radii of
colliding particles 1 and 2, then the bodies merge. For
impact velocities larger than $v_{mut, esc}$, no mass is transferred, and the bodies undergo a completely elastic bounce. 
Because the accretion outcome is all or nothing, this model should restrict growth more than a partial accretion model 
\citep{leinhardt12}. Below, we will show that the bounce-merge model does not meaningfully affect the outcome of the inner 
disk's planetesimal accretion phase, and so a partial accretion model should do the same.

@@

In this work, we have demonstrated that planetary embryo growth
can operate in two distinct modes in a planet-forming disk. In the first
mode, gravitational feedback from the growing embryos heats the
remaining planetesimals and results in a dynamically cold population
of embryos with a modest amount of residual planetesimals. This
corresponds to the ``oligarchic growth'' case revealed by \citep{kokubo98}, which is often used as a starting point for late-stage 
accretion models (e.g. \citet{kokubo02, raymond05, raymond06}). In the second mode, the gravitational feedback does not 
operate, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by 
oligarchic growth. The distinction between these modes is determined by ratio between the physical size of the bodies and their 
Hill radius, which sets the relative contribution of close gravitational encounters and collisions to the dynamical evolution of the 
disk.

>>>>

%TRQ: \sigma is not defined.
To ensure that the boundary seen near 60 days in orbital period is not
simply a transient product of the inside-out growth throughout the
disk, we examine the time evolution of $\sigma/\Sigma$ at multiple
orbital periods. In figure \ref{fig:pl_frac_time}, the value of
$\sigma/\Sigma$ is plotted as a function of time in 10 orbital period
bins, each with a width of 10 days.
Bins interior to 60 days are shown by a dashed line, while those exterior are shown as a solid line. In all radial bins, the 
planetesimal surface density is approaching an asymptotic value. In the inner disk, this value asymptotes to zero as the 
planetesimal population entirely depletes. In the outer disk, dynamical friction between the embryos and planetesimals 
eventually throttles subsequent accretion and leaves $\sim$ 10 percent or more of the mass surface density as planetesimals. It 
should be noted that in a typical oligarchic growth scenario, where protoplanets space themselves apart by 10 $r_{h}$ and settle 
onto circular orbits (giving $\tilde{b} = 2 \sqrt{3}$), roughly 30 percent of the planetesimal mass should remain out of reach of the 
protoplanets.({\bf citation here})

@@

Next, we investigate how the resulting planetesimal and protoplanet distribution
changes as we vary the initial solid surface density profile.
The final orbital period-eccentricity state of the
particles in the fdHi, fdHiSteep, fdHiShallow and fdLo simulations are shown in figure \ref{fig:surfden_profiles}, with point sizes 
indicating the relative masses of the bodies. In all cases, the inner disk is largely depleted of planetesimals, while the outer disk 
contains a bimodal population of planetesimals and embryos, with a clear separation in eccentricity between the two. Despite 
having significantly different masses, the planetary embryos formed in all simulations have remarkably similar eccentricities. This 
is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which 
offsets the fact that the initial bodies started off in a dynamically hotter state. The only exception to this is the fdLo simulation, 
where the resulting eccentricities are a couple orders of magnitude smaller. Inelastic damping likely plays an even more 
% TRQ: ??? the masses of the initial planetesimals are the same in all
% simulations according to table 1.
significant role here, due to the much larger masses of the initial planetesimals.

In figure \ref{fig:surfden_b}, we plot the masses of the resulting protoplanets and planetesimals in all four simulations in units of $
\tilde{b}$ (see equation \ref{eq:iso}). 
As mentioned previously, $\tilde{b} = 2 \sqrt{3}$ (indicated by the horizontal dashed line) carries a special significance, being the  
feeding zone width that a body on a circular orbit should have. In all four simulations, the feeding zone width exceeds the 
minimum value in the inner disk and approaches $2 \sqrt{3}$ beyond $\sim$ 60 days. The orbital periods at which this transition 
occurs are quite similar between simulations, despite the vastly different solid surface density profiles used. This indicates that 
the boundary between accretion modes is not dependent upon the surface density profile chosen, and also supports our 
conclusion that planetesimal accretion is largely complete everywhere in the disk.

@@

%TRQ: perhaps use a logarithmic horizontal axis for better comparison
\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/acc_zones.png}
    \caption{For the 20 most massive bodies at the end of the fdHi simulation, the relative shape of the accretion zones for each body are shown. The hash marks indicate the present position of the body. The accretion distributions indicate the initial locations of the planetesimals that were used to assemble a body, rather than the locations at which collisions with the massive body occurred.\label{fig:acc_zones}}
\end{center}
\end{figure*}

@@

Another line of evidence pointing to a lack of gravitational
scattering and orbital repulsion in the inner disk can be seen in
figure \ref{fig:acc_zones}. Here, we have chosen the 20 most massive
bodies from the fdHi simulation and arranged them in order of final
orbital period. On each line, the black
%TRQ: the mark is dark blue, not black.
hash mark indicates the present orbital period of an embryo and the gray histogram represents the initial orbital period distribution of the planetesimals which were used to construct the embryo. One should note that unlike the previous figure, this plot shows where every single bit of mass (in the form of planetesimals) originated, rather than only denoting embryo-planetesimal collisions.

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/f6f4_b.png}
    \caption{In the top panel, we show the required feeding zone sizes to produce the masses of the bodies seen
    at the end of the fdHi and fdHif4 simulations.  The bottom panel shows the variation of $\alpha$ with orbital period for the 
    bodies used in each case (solid curves). The orbital period at which $\alpha \simeq 0.1$ matches well with the intersection of 
    the embryo mass distribution and isolation mass. The shaded region
    in the bottom panel show the values of alpha for realistic-sized ($f=1$) planetesimals with bulk densities between 10 and 1 g cm$^{-3}$.\label{fig:f6f4_b}}
\end{center}
\end{figure}

@@

To test whether a more restrictive collision model should alter the growth mode of the inner disk, we ran a smaller scale test 
using a slightly more restrictive collision model. In this case, a collision can result in one of two outcomes: if the impact velocity is 
smaller than the mutual escape velocity of the colliding particles, defined as
\begin{equation}\label{eq:v_mut}
	v_{mut, esc} = \sqrt{\frac{2 G (m_{1} + m_{2})}{r_{1} + r_{2}}},
\end{equation}
where $m_{1}, m_{2}$ and $r_{1}, r_{2}$ are the masses and radii of
colliding particles 1 and 2, then the bodies merge. For
impact velocities larger than $v_{mut, esc}$, no mass is transferred, and the bodies undergo a completely elastic bounce. 
Because the accretion outcome is all or nothing, this model should restrict growth more than a partial accretion model 
\citep{leinhardt12}. Below, we will show that the bounce-merge model does not meaningfully affect the outcome of the inner 
disk's planetesimal accretion phase, and so a partial accretion model should do the same.

@@

In this work, we have demonstrated that planetary embryo growth
can operate in two distinct modes in a planet-forming disk. In the first
mode, gravitational feedback from the growing embryos heats the
remaining planetesimals and results in a dynamically cold population
of embryos with a modest amount of residual planetesimals. This
corresponds to the ``oligarchic growth'' case revealed by \citep{kokubo98}, which is often used as a starting point for late-stage 
accretion models (e.g. \citet{kokubo02, raymond05, raymond06}). In the second mode, the gravitational feedback does not 
operate, embryos quickly sweep up all planetesimals, and grow larger and less uniformly spaced than those produced by 
oligarchic growth. The distinction between these modes is determined
by the ratio between the physical size of the bodies and their 
Hill radius, which sets the relative contribution of close gravitational encounters and collisions to the dynamical evolution of the 
disk.
